Paper Title*\\ {\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and should not be used} \thanks{Identify applicable funding agency here. If none, delete this.}

### 2020-04-21 WorkSpace/Paper/Paper.tex
Expanded on method section, added appropriate references

% PACKAGES INCLUDED HERE 
% DO NOT NEED TO CHANGE
\documentclass[conference]{IEEEtran}
%\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{listings}
\usepackage{csquotes}
\usepackage{float}
\usepackage[caption=false]{subfig}
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

@@

% METHODS SECTION
\section{Methods}
\subsection{Seeding Method}
We went with a seed generation method that allowed a way to introduce some minor level of entropy to avoid letting the neural network aimlessly swim through the entropy of a strong seed instead of gaining stochastic insight on the data from the PRNG. \newline
The seed generation method we chose derives from the concept of using the system time as an element for seed generation. The specific implementation we chose took inspiration from Microsoft's .NET system.datetime.ticks property. [https://docs.microsoft.com/en-us/dotnet/api/system.datetime.ticks?view=netframework-4.8]. We chose to single out this method due to its documentation and unqiue simplicity. System time is widely used as a parameter for modern seed generation methods. To put it more trivially: "a pseudo random number generator is a deterministic algorithm that, given an initial number (called seed), generates a sequence of numbers that adequately satisfies statistical randomness tests. Since the algorithm is deterministic, the algorithm will always generate the exact same sequence of numbers if it's initialized with the same seed. That's why system time (something that changes all the time) is usually used as the seed for random number generators." (https://stackoverflow.com/users/33708/mehrdad-afshari) \newline
According to the Microsoft documentation, "A single tick represents one hundred nanoseconds or one ten-millionth of a second. There are 10,000 ticks in a millisecond, or 10 million ticks in a second. The value of this property represents the number of 100-nanosecond intervals that have elapsed since 12:00:00 midnight, January 1, 0001 in the Gregorian calendar."  \newline
We used a fairly similar Python port 
(https://stackoverflow.com/questions/29366914/what-is-python-equivalent-of-cs-system-datetime-ticks)
\lstset{language=Python}
\begin{lstlisting}[breaklines=true]
def ticks(dt):
    return (dt-datetime(1,1,1)).total_seconds()*10000000
\end{lstlisting}

@@

Additional changes we made to our implementation:
\begin{enumerate}
    \item Changing start time from January 1, 0001 to January 1, 1970, which effectively reduced the length of the seed for experimental purposes.
    \item Slicing last 6 digits of the ticks result to acquire more digit variation for frequent invocation.
\end{enumerate}
This final method allows enough spread between frequently retreived ticks, where we are assuming reasonable pseudo-unpredictabililty. This serves as a simplistic but constantly changing control mechanism for being able to seed PRNGs and test experimental outcomes. While not the most cryptographically strong, we needed a way to have some controlled aspect of seed generation to feed into generators of varying cryptographic complexity (to have some baseline of comparison).\newline

@@

@@

>>>>

% PACKAGES INCLUDED HERE 
% DO NOT NEED TO CHANGE
\documentclass[conference]{IEEEtran}
%\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{listings}
\usepackage{csquotes}
\usepackage{float}
\usepackage[caption=false]{subfig}
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{hyperref}
\usepackage{url}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

@@

% METHODS SECTION
\section{Methods}
\subsection{Seeding Method}
We went with a seed generation method that allowed a way to introduce some minor level of entropy to avoid letting the neural network aimlessly swim through the entropy of a strong seed instead of gaining stochastic insight on the data from the PRNG. \newline
The seed generation method we chose derives from the concept of using the system time as an element for seed generation. The specific implementation we chose took inspiration from Microsoft's .NET system.datetime.ticks property. \cite{b1} We chose to single out this method due to its documentation and unqiue simplicity. System time is widely used as a parameter for modern seed generation methods. To put it more trivially: "a pseudo random number generator is a deterministic algorithm that, given an initial number (called seed), generates a sequence of numbers that adequately satisfies statistical randomness tests. Since the algorithm is deterministic, the algorithm will always generate the exact same sequence of numbers if it's initialized with the same seed. That's why system time (something that changes all the time) is usually used as the seed for random number generators." \cite{b2} \newline
According to the Microsoft documentation, "A single tick represents one hundred nanoseconds or one ten-millionth of a second. There are 10,000 ticks in a millisecond, or 10 million ticks in a second. The value of this property represents the number of 100-nanosecond intervals that have elapsed since 12:00:00 midnight, January 1, 0001 in the Gregorian calendar." \cite{b1}  \newline
We used a fairly similar Python port, explained below. \cite{b3}
\lstset{language=Python}
\begin{lstlisting}[breaklines=true]
def ticks(dt):
    return (dt-datetime(1,1,1)).total_seconds()*10000000
\end{lstlisting}

@@

Additional changes we made to our implementation:
\begin{enumerate}
    \item Changing start time from January 1, 0001 to January 1, 1970, which effectively reduced the length of the seed for experimental purposes.
    \item Slicing last 6 digits of the ticks result to acquire more digit variation for frequent invocation.
\end{enumerate}

This final method allows enough spread between frequently retreived ticks, where we are assuming reasonable pseudo-unpredictabililty. This serves as a simplistic but constantly changing control mechanism for being able to seed PRNGs and test experimental outcomes. While not the most cryptographically strong, we needed a way to have some controlled aspect of seed generation to feed into generators of varying cryptographic complexity (to have some baseline of comparison).\newline

@@

\subsection{PRNG Implementations}
\subsection{Predictive Network}
The predictor is a convolutional neural network implementing the function
: $P(r_{split}) \mathbb{B}$ 7→B(7)wherersplitis  the  generator’s  output  vector  with  the  last  element  removed.The  last  element  is  used  as  the  corresponding  label  for  the  predictor’s  input.
\begin{figure}[H]
\centering
\includegraphics[width=1\linewidth]{./Images/PredictiveModel.png}
\caption{Predictive Model}
\label{fig:globfig}
\end{figure}

\subsection{Experimental Setup}
\begin{figure}[H]
\centering
\includegraphics[width=1\linewidth]{./Images/ModelDiagram.png}
\caption{Experiment Model}
\label{fig:globfig}
\end{figure}

@@

.. code:: ipython3

    % REFERENCES
    % THIS IS CREATED AUTOMATICALLY
    \bibliographystyle{IEEEtran}
    \bibliography{References} % change if another name is used for References file
